Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
image AWS

\abstract{The use of accelerators in order to reduce the execution time of some 
application has become more popular during last years. These devices increment 
the computational power of a computer thanks to its parallel architecture. %The popularity of the GPGPU computation 
This trend has led several cloud vendors such as Amazon Web Services or some 
middlewares such as OpenStack to add to their current facilities, or to allow, 
instances of virtual machines equipped with NVIDIA GPUs. 
Accomplishing this requirements needs that the guest hosts must be equipped with 
GPUs which could be barely utilized if a non GPU-enabled Virtual Machine is running in the host.
The solution presented in this work is based on GPU virtualization and shareability 
in order to reach an equilibrium between supply and demand of accelerators from the users. 
Hence, we propose to decouple, from the nodes, real GPUs by using the virtualization technology. 
So, these GPUs can be accessed from any VM getting rid of the necessity of having physical 
GPUs in the guest host. 
Moreover, our project studies the viability of these join by using a public cloud 
service configuration and develops a module for OpenStack middleware in order to 
add the needed support for the virtualized devices.  
%goes further and it takes into account that by making logical 
%partitions of the GPU memory we could address each partition as if it was an 
%independent GPU device.
}

@@

\section{Remote GPUs in AWS}
\label{sec:rgpuaws}

\begin{itemize}
\item Escenarios creados
\item Experimentos
\item An\'alisis basados en flexibilidad y coste econ\'omico
\end{itemize}

\section{GPGPU Service for OpenStack}
\subsection{Managing remote GPUs with OpenStack}
The main idea of this project is to reach a solution that drive us to an scenario pretty similar the one that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
>>>>>>> b29156d83b82f6d0c9490cadc106cdbd54178d8e
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.

>>>>

\abstract{The use of accelerators in order to reduce the execution time of some 
application has become more popular during last years. These devices increment 
the computational power of a computer thanks to its parallel architecture. %The popularity of the GPGPU computation 
This trend has led several cloud vendors such as Amazon Web Services or some 
middlewares such as OpenStack to add to their current facilities, or to allow, 
instances of virtual machines equipped with NVIDIA GPUs. 
Accomplishing this requirements needs that the guest hosts must be equipped with 
GPUs which could be barely utilized if a non GPU-enabled Virtual Machine is running in the host.
The solution presented in this work is based on GPU virtualization and shareability 
in order to reach an equilibrium between supply and demand of accelerators from the users. 
Hence, we propose to decouple, from the nodes, real GPUs by using the virtualization technology. 
So, these GPUs can be accessed from any VM getting rid of the necessity of having physical 
GPUs in the guest host. 
Moreover, our project studies the viability of these join by using a public cloud 
service configuration and develops a module for OpenStack middleware in order to 
add the needed support for the virtualized devices and the logic to manage them.  
%goes further and it takes into account that by making logical 
%partitions of the GPU memory we could address each partition as if it was an 
%independent GPU device.
}

@@

\section{Working with Remote GPUs in AWS}
\label{sec:rgpuaws}

\begin{itemize}
\item Esc\begin{figure}[!t]
  \centering
  \includegraphics[width=\linewidth]{images/AWS.pdf}
  \caption{An AWS instance with 13 remote GPUs}
  \label{fig:aws1}
\end{figure}enarios creados

\item Experimentos
\item An\'alisis basados en flexibilidad y coste econ\'omico
\end{itemize}

\section{GPGPU Shared Service in OpenStack}
In this section is explained all the work related to OpenStack that has been done, from the development of an external module to handle remote GPUs to the physical setup and its testing.
\subsection{Managing remote GPUs with OpenStack}
The main idea of this solution is to reach the scenario that could be seen in Figure~\ref{fig:external}, where a new shared service takes part in to the OpenStack Architecture.
This new service is in charge of GPGPU computation, bringing more flexibility when it comes to GPUs.
As it is shown in Figure~\ref{fig:internal}, we have altered the OpenStack original Dashboard with a new parser, 
which split the HTTP query in order to make use of both, the GPGPU API for everything related to GPUs, and the nova API for the rest of the computation. 
The new GPGPU Service has brought a new feature which brings more flexibility when managing GPUs, from now on, we can create ``GPU-pools''. 
A ``GPU-pool'' is a set of independent GPUs (logically disattached from the nodes) that can be assigned to one or more instances.
